### 2013-05-14 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
adding mcsa breakdown data spreadsheet

\subsubsection{Domain Leakage}
\label{subsubsec:domain_leakage}
Finally, we seek to measure the leakage from a domain in a domain
decomposed Monte Carlo calculation and assess the quality of our
analytic relation for the optical thickness of domain and the
associated leakage approximations. For this experiment, a square grid
with $h=0.1$ was decomposed into 9 square domains, 3 in each cardinal
direction with measurements occurring in the central domain without
boundary grid points. For the cross subsections, the absorption cross
subsection was varied from 1 to 100 while the scattering cross subsection
was set to zero to create a purely absorbing environment with weight
cutoff of \sn{1}{-4}. The optical thickness of these domains will vary
as a function of the absorption cross subsection if the other parameters
are fixed. To compute the optical thickness, along with the spectral
radius as given by Eq~(\ref{eq:iteration_radius}), we also need the
parameters $n_i$ and $n_s$ which respectively describe the typical
domain length and the average number of states moved along that
typical length per history transition. For our grid above, the domains
are varied in size with $50 \times 50$, $100 \times 100$, and $200
\times 200$ cells giving $n_i=50$, $n_i=100$, and $n_i=200$ grid
points or states along the typical length of the domain
respectively. Looking at the Laplacian stencil in
Eq~(\ref{eq:nine_point_stencil}), we see that all history transitions
will only move a single state in either the $i$ or $j$ directions due
to the symmetry of the problem. Furthermore, if we choose the $i$
direction, not all states we will transition to will move the history
in that direction. Therefore, we look to the definition of the
iteration matrix in Eq~(\ref{eq:iteration_stencil}) and the definition
of the adjoint probability matrix in Eq~(\ref{eq:adjoint_probability})
to estimate the $n_s$ parameter. For a particular transition starting
at state $(i,j)$, 6 of the 8 possible new states in the stencil move
the history in $i$ direction with relative coefficients of 4 for
moving in the $(\pm i,0)$ direction and of 1 for moving in the $(\pm
i,\pm j)$. These coefficients dictate the frequency those states are
visited relative to the others. For those 6 states we can visit along
the typical length, their sum is 12 out of the total 20 for the
coefficients for all possible states with their ratio giving $n_s =
\frac{3}{5}$.

>>>>

\subsubsection{Domain Leakage}
\label{subsubsec:domain_leakage}
Finally, we seek to measure the leakage from a domain in a domain
decomposed Monte Carlo calculation and assess the quality of our
analytic relation for the optical thickness of a domain and the
associated leakage approximations. For this experiment, a square grid
with $h=0.1$ was decomposed into 9 square domains, 3 in each cardinal
direction with measurements occurring in the central domain without
boundary grid points. For the cross subsections, the absorption cross
subsection was varied from 1 to 100 while the scattering cross
subsection was set to zero to create a purely absorbing environment
with weight cutoff of \sn{1}{-4}. The optical thickness of these
domains will vary as a function of the absorption cross subsection if
the other parameters are fixed. To compute the optical thickness,
along with the spectral radius as given by
Eq~(\ref{eq:iteration_radius}), we also need the parameters $n_i$ and
$n_s$ which respectively describe the typical domain length and the
average number of states moved along that typical length per history
transition. For our grid above, the domains are varied in size with
$50 \times 50$, $100 \times 100$, and $200 \times 200$ cells giving
$n_i=50$, $n_i=100$, and $n_i=200$ grid points or states along the
typical length of the domain respectively. Looking at the Laplacian
stencil in Eq~(\ref{eq:nine_point_stencil}), we see that all history
transitions will only move a single state in either the $i$ or $j$
directions due to the symmetry of the problem. Furthermore, if we
choose the $i$ direction, not all states we will transition to will
move the history in that direction. Therefore, we look to the
definition of the iteration matrix in Eq~(\ref{eq:iteration_stencil})
and the definition of the adjoint probability matrix in
Eq~(\ref{eq:adjoint_probability}) to estimate the $n_s$ parameter. For
a particular transition starting at state $(i,j)$, 6 of the 8 possible
new states in the stencil move the history in $i$ direction with
relative coefficients of 4 for moving in the $(\pm i,0)$ direction and
of 1 for moving in the $(\pm i,\pm j)$. These coefficients dictate the
frequency those states are visited relative to the others. For those 6
states we can visit along the typical length, their sum is 12 out of
the total 20 for the coefficients for all possible states with their
ratio giving $n_s = \frac{3}{5}$.
